Homework 3

### 2019-09-19 hw3/MSimonsHW3.tex
problem 2 hw 3

>>>>

\item The set $\frac{1}{2}\mathbb{Z}$ is not a ring.  A ring must be closed under
multiplication.  Let $a = \frac{m}{2}$ and $b = \frac{n}{2}$ for some integers
$m$, $n$.  We know that $ab = \frac{mn}/4$.  Assume $m$ and $n$ are both odd and
that $m = 2x + 1$ and $n = 2y + 1$ for some integers $x$, $y$.  Therefore,
\[
ab = \frac{mn}{4} = \frac{(2x+1)(2y+1)}{4} = \frac{2(2xy+y)+1}{4}
\]
Since $ab$ is not an element of the set, this means that the set is not closed
under multiplication.

\item This set is a ring. \\
Let $a = \frac{m}{2x+1}$, $b=\frac{n}{2y+1}$, $c=\frac{l}{2z+1}$ be elements of
the set for some integers $m$, $n$, $l$, $x$, $y$, and $z$.\\
The set is closed under addition:
\[
a + b = \frac{m}{2x+1} + frac{n}{2y+1} = \frac{m(2y+1) + 2(nx+1)}{2(2xy+x+y)+1}
\]
Associative addition holds:
\[
a+(b+c) = \frac{m}{2x+1} + (\frac{n}{2y+1} + \frac{l}{2z+1})
\]
\[
= \frac{m(2y+1)(2z+1) + n(2z+1)(2x+1) + l(2y+1)(2x+1)}{(2x+1)(2y+1)(2z+1)}
\]
\[
= (\frac{m}{2x+1} + \frac{n}{2y+1}) + \frac{l}{2z+1} = (a+b)+c
\]
Commutative addition holds:
\[
a + b = \frac{m}{2x+1} + \frac{n}{2y+1}
\]
\[
= \frac{m(2y+1) + 2(nx+1)}{2(2xy+x+y)+1}
\]
\[
= \frac{n}{2y+1} + \frac{m}{2x+1} = b + a
\]
There exists an $0$ element in the set such that:
\[
a + 0 = \frac{m}{2x+1} + \frac{0}{1} = \frac{m}{2x+1} = a
= \frac{0}{1} + \frac{m}{2x+1} = 0 + a
\]
There is a solution to $a + x = 0$.  Let $x = \frac{-m}{2x+1}$:
\[
a + x = \frac{m}{2x+1} + \frac{-m}{2x+1} = \frac{m + {-m}}{2x+1} = \frac{0}{2x+1} = 0
\]
The set is closed under multiplication:
\[
ab = \frac{m}{2x+1}\cdot\frac{n}{2y+1} = \frac{mn}{(2x+1)(2y+1)} = \frac{mn}{2(2xy+x+y)+1}
\]
Associative multiplication holds:
\[
a(bc) = \frac{m}{2x+1}\cdot(\frac{n}{2y+1}\cdot\frac{l}{2z+1}) = (\frac{m}{2x+1}\cdot\frac{n}{2y+1})\cdot\frac{l}{2z+1}
= (ab)c
\]
The Distributive Property holds:
\[
a(b+c) = \frac{m}{2x+1}\cdot(\frac{n}{2y+1}+\frac{l}{2z+1})
= \frac{m}{2x+1}\cdot(\frac{n(2z+1) + l(2y+1)}{(2y+1)(2z+1)})
\]
\[
= \frac{m}{2x+1}\cdot\frac{n}{2y+1} + \frac{m}{2x+1}\cdot\frac{l}{2z+1}
=ab+ac
\]
